Neural Neural Textures Make Better Simulators ``I Can't Believe It's Not Real!''

### 2022-06-16 CORL/example.tex
Why wont it push images

		To keep the object surfaces consistent, we impose a pixel-wise ``unprojection consistency loss'' by unprojecting surfaces in fake photos back into the common texture space.
% 		\begin{equation}
% 			u\toNL=\text{unproject}(\ph\toN,s\toN)   \eqand  \lUC \Rightarrow u_1 \approx u_2 \dots \approx u_N
% 		\end{equation}
        Given a UVL scene $s$ and its respective fake photo $\ph$, the unprojection $\unprojection$ is obtained from assigning $(r,g,b)$ values at each pixel location $(x, y)$ of $\ph$ to its corresponding $(u, v, l)$ coordinates according to $s$. 
        % That is, we convert $s$ and $\ph$ to a key-value dictionary where the key is $(u,v,l)$ and the value is $(r,g,b)$, and such dictionary is $\unprojection$.
        For simplicity, we note
        \begin{equation}
            	\unprojection_{[u,v]}^{l}=\expectation\ph_{[x,y]} \quad s.t.~ (u,v,l) = s_{[x,y]},
        \end{equation}
        where the expectation $\mathbb{E}$ means we aggregate multiple $(r,g,b)$ vectors being assigned to the same $(u,v,l)$ location by averaging them. 
        In practice, $(u,v,l)$ are real numbers between $[0,1]$, where as each $\unprojection$ have to be rasterized, i.e represented by $L$ $(128\times 128\times 3)$ images, where $L$ is the number of labels and $128\times 128$ is the resolution of the unprojection. Therefore, we discretize and scale corresponding $(u,v,l)$ to integers so that each $(r,g,b)$ vector will be assigned to a pixel on $\unprojection$. For the exact implementation, please see our supplementary material.

        We obtain $N$ unprojections $\{\unprojection_{[u,v]}^{l,i}\}_{i=1}^{N}$ from a batch of $N$ UVL scenes and fake photos. The unprojection consistency loss is defined as the per-pixel
        \begin{equation}

        \end{equation}

		%We sample a random batch of UVL scenes $S\toN$, and translate them into $\ph\toN$.
		%Using geometric knowledge of the scene encoded in $S\toN$, we individually unproject each $\ph^i \in \ph\toN$ back into texture space, to obtain $N$ sets of $L$ unprojected textures $u\toNL$.
		%We then use the per-pixel, batch-wise standard deviation of the unprojections as unprojection consistency loss $\lUC = \sigma(u\toNL)\toL$.
		%This loss observes how different these unprojections are from one another, and thus how different the object surfaces appear between translations.

		Intuitively, if $\lUC$ were $0$, it would mean the object surfaces in translations $\ph$ appear exactly the same in every scene.

>>>>

		To keep the object surfaces consistent, we impose a pixel-wise ``unprojection consistency loss'' by unprojecting surfaces in fake photos back into the common texture space.
% 		\begin{equation}
% 			u\toNL=\text{unproject}(\ph\toN,s\toN)   \eqand  \lUC \Rightarrow u_1 \approx u_2 \dots \approx u_N
% 		\end{equation}
        Given a UVL scene $s$ and its respective fake photo $\ph$, the unprojection $\unprojection$ is obtained from assigning $(r,g,b)$ values at each pixel location $(x, y)$ of $\ph$ to its corresponding $(u, v, l)$ coordinates according to $s$. 
        % That is, we convert $s$ and $\ph$ to a key-value dictionary where the key is $(u,v,l)$ and the value is $(r,g,b)$, and such dictionary is $\unprojection$.
        For simplicity, we note
        \begin{equation}
            	\unprojection_{[u,v]}^{l}=\expectation\ph_{[x,y]} \quad s.t.~ (u,v,l) = s_{[x,y]},
        \end{equation}
        where the expectation $\mathbb{E}$ means we aggregate multiple $(r,g,b)$ vectors being assigned to the same $(u,v,l)$ location by averaging them. 
        In practice, $(u,v,l)$ are real numbers between $[0,1]$, where as each $\unprojection$ have to be rasterized, i.e represented by $L$ $(D\times D\times 3)$ images, where $L$ is the number of labels and $D\times D$ is the resolution of the unprojection. Therefore, we discretize and scale corresponding $(u,v,l)$ to integers so that each $(r,g,b)$ vector will be assigned to a pixel on $\unprojection$. For the exact implementation, please see our supplementary material.

        We obtain $N$ unprojections $\{\unprojection_{[u,v]}^{l,i}\}_{i=1}^{N}$ from a batch of $N$ UVL scenes and fake photos. The unprojection consistency loss is defined as the per pixel-channel standard deviation of $\unprojection$ over the batch
        \begin{equation}
            \ell_{UC} = \frac{1}{L\times D\times D\times 3}\sum_{l,u,v,c}\sigma(\{\unprojection^{l,i}_{[u,v,c]}\}_{i=1}^{N}),
        \end{equation}
        where $\sigma(\cdot)$ stands for the variance function and $c \in \{1\dots 3\}$ is the channel index of $\unprojection$.
		%We sample a random batch of UVL scenes $S\toN$, and translate them into $\ph\toN$.
		%Using geometric knowledge of the scene encoded in $S\toN$, we individually unproject each $\ph^i \in \ph\toN$ back into texture space, to obtain $N$ sets of $L$ unprojected textures $u\toNL$.
		%We then use the per-pixel, batch-wise standard deviation of the unprojections as unprojection consistency loss $\lUC = \sigma(u\toNL)\toL$.
		%This loss observes how different these unprojections are from one another, and thus how different the object surfaces appear between translations. 
		We minimize $\lUC$ to encourage unprojections to be consistent across the batch. Intuitively, if $\lUC$ were $0$, it would mean the object surfaces in translations $\ph$ appear exactly the same in every scene. In addition, we call the mean of unprojections $\mu(\{\unprojection^{(l,i)}\}_{i=1}^N)$ as ``Recovered Textures'', visualzed in Figure~\ref{fig:first_diagram} and \ref{fig:unprojection_consistency_loss}.
